Verifying Demonstrations

### 2017-08-27 properties.tex
Improves slides by successively constructing fig

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's and Bob's proofs.

@@

      \item Physical transportation is limited.
      \item Accuracy of Alice's witnessing is proportional to time from Jane's 
        witnessing.
    \end{itemize}
  \end{idea}

  \begin{remark}
    \begin{itemize}
      \item Alice's signature key must have the physical travel properties, 
        embedded in hardware.
      \item Alice's witness signature must depend on Jane's.
      \item High-precision relation to time?
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=right,level distance=5em}
    \Tree [.Proof
      [.{wsig} {\(x,y\)} [.{\mode<presentation>{\only<1>{\color{red}}} osig} 
      [.{\mode<presentation>{\only<2>{\color{red}}}\(id\)} manifesto ] head ] 
      [.tsig head$'$ ] ]
      {\dots}
      [.{wsig} {\dots} ]
    ]
  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

>>>>

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \centering
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  \end{figure}

  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within the protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}
}

@@

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's proof.

@@

      \item Alice witnesses Bob's proof.
      \item Alice's (secret key's) transportation is physically limited.
      \item Trust on Bob's proof is proportional to time from when Jane 
        witnessed Alice's proof.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}
  \begin{figure}
    \centering
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}tsig} {$t_s'$} ] ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  \end{figure}

  \begin{remark}
    \begin{itemize}
      \item Secret key in hardware.
      \item Alice's witness signature must depend on Jane's.
      \item High-precision relation to time?
    \end{itemize}
  \end{remark}
\end{frame}
}

@@

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ] [.tsig 
        {$t_s''$} ] ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ] [.tsig 
      {$t_s''$} ] ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}
